Hippocampal replay of experience at real-world speeds

### 2020-10-08 Article.tex
Update on Overleaf.

Surprisingly, our results indicate that most events with coherent spatial content are not dominated by the continuous movement dynamic, and thus correspond to trajectories that are stationary or that move relatively slowly compared to their purely continuous counterparts. We therefore examined these events in more detail. We first note that most of the SWRs (16454 of 23382 classified SWRs or 70\%) are well described by a single dynamic or mixtures of dynamics (Figure \ref{5}A). Surprisingly, the most common category is stationary-continuous mixtures (9860 of 23382 classified SWRs or 42\%, Figure \ref{5}A). These events contain representations that move at slower speeds (Figure \ref{5}D; though note these speeds are calculated from the MAP estimate and thus noisy), and are slightly shorter, on average, than events with continuous dynamics (median duration: stationary-continuous-mixture 72 ms vs. continuous 95 ms, Figure \ref{5}B). Nonetheless, both these slow-moving events and continuous events represented locations that were some distance away from the animal (mean trajectory distance from animal's position: stationary-continuous-mixture 51 cm vs. continuous 42 cm, Figure \ref{5}C). This indicates that the trajectories of these SWRs, like ones that have faster continuous dynamics, do not represent the animal's actual position and cannot be explained by erroneously detected SWRs.

@@

%TC:endignore
%the command above ignores this section for word count

>>>>

Surprisingly, our results indicate that most events with coherent spatial content are not dominated by the continuous movement dynamic, and thus correspond to trajectories that are stationary or that move relatively slowly compared to their purely continuous counterparts. We therefore examined these events in more detail. We first note that most of the SWRs (16454 of 23382 classified SWRs or 70\%) are well described by a single dynamic or mixtures of dynamics (Figure \ref{5}A). Surprisingly, the most common category is stationary-continuous mixtures (9860 of 23382 classified SWRs or 42\%, Figure \ref{5}A, Figure\ref{fig:Figure5-Figure supplement 1}). These events contain representations that move at slower speeds (Figure \ref{5}D; though note these speeds are calculated from the MAP estimate and thus noisy), and are slightly shorter, on average, than events with continuous dynamics (median duration: stationary-continuous-mixture 72 ms vs. continuous 95 ms, Figure \ref{5}B). Nonetheless, both these slow-moving events and continuous events represented locations that were some distance away from the animal (mean trajectory distance from animal's position: stationary-continuous-mixture 51 cm vs. continuous 42 cm, Figure \ref{5}C). This indicates that the trajectories of these SWRs, like ones that have faster continuous dynamics, do not represent the animal's actual position and cannot be explained by erroneously detected SWRs.

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure5-supplemental1/Figure5_v1-supplemental1}
\caption{More examples of stationary-continuous-mixtures.}
\label{fig:Figure5-Figure supplement 1}
\end{figure*}
%TC:endignore
%the command above ignores this section for word count
